Dancing on Water: The Choreography of Sulfur Dioxide Adsorption to Aqueous Surfaces

### 2011-07-04 Introduction.tex
Draft 9

An important gas for developing a picture of gaseous adsorption and entry into a water surface is sulfur dioxide.\cite{Lattanzi2010,Shah2011,Tzivian2011,Johns2011,Faloona2009,Jurkat2010,Wu2011} \suldiox~enters the environment as an important industrial product, and also naturally through terrestrial processes. Atmospheric dust particles and gases have been implicated in the oxidation of \suldiox, and act as reaction surfaces for chemical mechanisms that are still poorly understood.\cite{Baltrusaitis2011,Rubasinghege2010,Li2007} \suldiox~acts as a major component of atmospheric pollution, and is a precursor to acid rain formation, and cloud nucleation. Its high solubility in water makes \suldiox~an integral compound in many aqueous atmospheric reactions, as well.  Obtaining a more complete picture of the \suldiox~adsorption process is important for understanding gaseous adsorption of this environmentally important gas on water and aerosol surfaces as well as being a model system for understanding the more general nature of gases at aqueous interfaces.

>>>>

An important gas for developing a picture of gaseous adsorption and entry into a water surface is sulfur dioxide.\cite{Lattanzi2010,Shah2011,Tzivian2011,Johns2011,Faloona2009,Jurkat2010,Wu2011,Jayne1990,Yang2002} \suldiox~enters the environment as an important industrial product, and also naturally through terrestrial processes. Atmospheric dust particles and gases have been implicated in the oxidation of \suldiox, and act as reaction surfaces for chemical mechanisms that are still poorly understood.\cite{Baltrusaitis2011,Rubasinghege2010,Li2007,Madsen2008,Boniface2000} \suldiox~acts as a major component of atmospheric pollution, and is a precursor to acid rain formation, and cloud nucleation. Its high solubility in water makes \suldiox~an integral compound in many aqueous atmospheric reactions, as well.  Obtaining a more complete picture of the \suldiox~adsorption process is important for understanding gaseous adsorption of this environmentally important gas on water and aerosol surfaces as well as being a model system for understanding the more general nature of gases at aqueous interfaces.

### 2011-07-04 Methods.tex
Draft 9

	To overcome this problem we define the water surface location by calculating a reference location at each time step by averaging the positions of the waters contained in the topmost monolayer. This provides a consistent and intuitive reference point in the simulations to which we relate our analyses, but does not increase the computational burden. The number of waters included in the averaging is determined by taking a few issues into account. First, counting the waters found in the topmost cross-section of the water slab over several time steps indicated between 65-75 waters that established a full monolayer. This was done by a visual inspection of the slab using the VMD MD visualization package.\cite{HUMP96} Alternatively, assuming a spherical model of water with a radius of 2.2\angs~(the typical length of a bulk-water hydrogen bond), two layers of hexagonally tight-packed spheres yielded a similar number of surface water molecules. Increasing the number of waters used in calculating the surface location diminishes the effects of the few waters that briefly rise above the surface into the gas phase, stabilizing both the surface position and thickness values. Taking the close-packed model as a maximum number of waters fit into a flat surface, the topmost 70 water molecules were used for calculating instantaneous water surface locations for each simulation step.

>>>>

	To overcome this problem we define the water surface location by calculating a reference location at each time step by averaging the positions of the waters contained in the topmost monolayer. This provides a consistent and intuitive reference point in the simulations to which we relate our analyses, but does not increase the computational burden. The number of waters included in the averaging is determined by taking a few issues into account. First, counting the waters found in the topmost cross-section of the water slab over several time steps indicated between 65-75 waters that established a full monolayer. This was done by a visual inspection of the slab using the VMD MD visualization package.\cite{Humphrey1996} Alternatively, assuming a spherical model of water with a radius of 2.2\angs~(the typical length of a bulk-water hydrogen bond), two layers of hexagonally tight-packed spheres yielded a similar number of surface water molecules. Increasing the number of waters used in calculating the surface location diminishes the effects of the few waters that briefly rise above the surface into the gas phase, stabilizing both the surface position and thickness values. Taking the close-packed model as a maximum number of waters fit into a flat surface, the topmost 70 water molecules were used for calculating instantaneous water surface locations for each simulation step.
